---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# censlm

<!-- badges: start -->
<!-- badges: end -->

The goal of censlm is to simplify fitting censored linear models and using
them to draw plausible imputed values for censored observations.

## Installation

You can install the development version of censlm like so:

``` r
remotes::install_github("mikmart/censlm")
```

## Example

Fit a censored linear model to left-censored data with `clm()`, then draw random
values for censored observations from the fitted distribution with `imputed()`:

```{r example}
library(censlm)
set.seed(42)

# Simulate left-censored log-normal CRP observations
crp <- rlnorm(10000, 1.355, 1.450)
lloq <- 3
obs <- replace(crp, crp < lloq, lloq)
crpdf <- data.frame(crp, lloq, obs)

# Fit censored linear model and extract (random) imputations
fit <- clm(log(obs) ~ 1, left = log(lloq))
imp <- exp(imputed(fit))

summary(fit)
summary(cbind(crpdf, imp))
```
